Collaborative Visual Analysis on the Web with RCloud

### 2015-03-31 introduction.tex
working
copy editing

Unfortunately, the processes and technologies supporting data analysis visual analytics are fragmented.
Knowledge is shared through informal conversations, emails,
meetings, phone calls, source code itself, in wikis, in project documents and
by other means. Results of experiments are often shared first by copying static
output (usually a simple screen shot or image output). By the time
decisions are made based on the results of that screenshot, the data
and the processes might have changed enough to bring to question the
original decision.

@@

This situation can affect how data science teams; as analysts and
toolbuilders, we have experienced this first-hand in our environment, and
others report similar findings. Gutierrez collected interviews with data
scientists~\cite{Gutierrez:2014:DSA}, which include the following:

\begin{itemize}
\item (upon being given access to other code and data analysis, in
order to learn about Hadoop) ``[...] Not only that, I could also look at other people’s code and
play with their code and data sets as well''
\item (discussing the value of sharing prototypes rather than static
data) ``[...] Finally, prototyping our products so that internal
customers can use them early on has been crucial for
our success. [...] Now we can shoot off a URL to internal
customers and it allows them to [...] provide feedback way before
we're talking about getting it into production.''
\item (on sharing more than just a finished product) ``We also share
exploratory analyses and reports [...] so that we can still exchange
knowledge even if the work didn't make it into a larger project.''
\item (on changing analyses and processes) ``It is important to
have testing frameworks for all of your data, so [...] you can go back and test all
of your data. 
\end{itemize}

Currently, these concerns need to be addressed \emph{alongside} the
visual analytics environment. Some symptoms of the current situation are:
\begin{itemize}
\item It is hard to find data, metadata, and knowledge about them.
\item Most coordination is done through meetings, whose content is not linked to other artifacts and may not even be stored.
\item Production deployment requires porting code to a different environment or even completely rewriting it, thwarting continuous release.
\item Many tools adopt a standalone or single developer perspective,
not suited to collaboration and web deployment. 
\item Analysts find insufficient support for tracing events or issues from production back to the EDA process.
\end{itemize}

@@

A key point is that, for the most part, the improved capabilities are
available by default, without much explicit intervention on the part of
data scientists and other customers. Visual analytics experiments are
conveniently shared and turned into production websites, without moving
or porting code. All the published artifacts in the system can be
searched immediately. Recommendation is as easy as clicking a star
on a useful workbook.

@@

From a more principled or theoretical perspective, certain visual analytics
goals or objectives for emerging systems, described in previous work,
closely match ours. We noted the following central themes.

@@

\carlos{we need a segue into related work}.

>>>>

Unfortunately, the processes and technologies supporting data analysis visual analytics are fragmented.
Knowledge is shared through informal conversations, emails,
meetings, phone calls, source code, in wikis, project documents and
by other means. Results of experiments are often shared first by copying static
output, usually a screen shot or image output. By the time
decisions are made based on the results of that screenshot, data
and processes may have changed so much that the decision can be wrong.

@@

This situation can affect how data science teams work; as analysts and
tool builders, we have experienced this first-hand in our environment, and
others report similar findings. Gutierrez collected interviews with data
scientists~\cite{Gutierrez:2014:DSA}, which include the following:

\begin{itemize}
\item (upon being given access to other code and data analysis, in
order to learn about Hadoop) ``I could look at other people’s code
and play with their code and data sets as well''
\item (discussing the value of sharing prototypes rather than static
data) ``Prototyping our products so that internal
customers can use them early on has been crucial for
our success. Now we can shoot off a URL to internal
customers and it allows them to provide feedback way before
we're talking about getting it into production.''
\item (on sharing more than just a finished product) ``We also share
exploratory analyses and reports so that we can still exchange
knowledge even if the work didn't make it into a larger project.''
\item (on changing analyses and processes) ``It is important to
have testing frameworks so you can go back and test all
of your data.''
\end{itemize}

Currently, these concerns are being addressed \emph{alongside} the
visual analytics environment. Some symptoms of the situation are:
\begin{itemize}
\item It is hard to find data, metadata, and knowledge about them.
\item Most coordination is done through meetings, whose content is not linked to other artifacts and may not even be stored.
\item Production deployment requires porting code to a different environment or even completely rewriting it, thwarting continuous release.
\item Many tools adopt a standalone or single developer perspective,
not suited to collaboration and web deployment. 
\item Analysts find insufficient support for tracing events or issues from production back to the EDA process.
\end{itemize}

@@

A key point is that, for the most part, the improved capabilities are
available by default, without much explicit involvement on the part of
data scientists and other customers. Visual analytics experiments are
conveniently shared and turned into production websites, without moving
or porting code. All the published artifacts in the system can be
searched immediately. Recommendation is as easy as clicking a star
on a useful workbook.

@@

From a more principled or theoretical perspective, certain visual analytics
goals or objectives for emerging systems, described in previous work,
closely match ours. We identified the following central themes.

@@

%\carlos{we need a segue into related work}.
%\stephen{maybe not?}
